---
output: 
  github_document:
    toc: false
    fig_width: 10.08
    fig_height: 6
tags: [r, reports]
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  dpi = 600,
  collapse = TRUE,
  fig.path = "img/"
)
options(
  knitr.kable.NA = "",
  digits = 4,
  width = 60
)

library(tidyverse)
```





# Publications

- [**Personal Website**](https://dominiquemakowski.github.io/)
- [**List of Communications**](https://github.com/DominiqueMakowski/publications#communications)

This repo contains materials related to my publications (such as data and analysis scripts) to facilitate reproducibility and sharing.


## Research 

My research wordcloud, based on the most frequent words of my papers (done using R).

<p align="center">
```{r wordcloud, echo = FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.align='center'}
library(ggwordcloud)
library(pdftools)


replace_and_add <- function(data, target, add_to, delete = T) {
  if (!add_to %in% data$word) {
    data[nrow(data) + 1, ] <- c(add_to, 0)
  }
  data <- data %>%
    mutate(
      newfreq = freq[word == target],
      newfreq = replace(newfreq, !(word %in% c(add_to)), 0),
      freq = as.numeric(freq) + as.numeric(newfreq)
    ) %>%
    select(-newfreq)

  if (delete == T) {
    data <- filter(data, word != target)
  }
  return(data)
}

# ------------------------------

sources <- list.files(path = "./papers", pattern = "pdf$")


text <- c()
for (source in sources) {
  text <- c(text, pdftools::pdf_text(paste("./papers/", source, sep = "")))
}

text <- unlist(text)
text <- paste(text, sep = " ", collapse = "")
text <- iconv(text, "UTF-8", "ASCII", sub = "")


text_clean <- tm::termFreq(text, control = list(removePunctuation = TRUE, tolower = TRUE, removeNumbers = TRUE, stopwords = TRUE, wordLengths = c(2, Inf)))

data <- data.frame(word = rownames(as.matrix(text_clean)), freq = rowSums(as.matrix(text_clean))) %>%
  arrange(desc(freq)) %>%
  replace_and_add("er", "emotion", delete = F) %>%
  replace_and_add("er", "regulation") %>%
  replace_and_add("emotional", "emotion") %>%
  replace_and_add("psychologie", "psychology") %>%
  replace_and_add("psychologique", "psychological") %>%
  replace_and_add("mditation", "meditation") %>%
  replace_and_add("ction", "fiction") %>%
  replace_and_add("ctional", "fiction") %>%
  dplyr::mutate(length = stringr::str_length(word)) %>%
  dplyr::filter(freq > 30) %>%
  dplyr::filter(freq < Inf) %>%
  dplyr::filter(length >= 4) %>%
  dplyr::select(-length) %>%
  dplyr::filter(!word %in% c("dans", "plus", "pour", "avec", "cette", "comme", "sont", "tion", "also", "france", "nature", "lhrdit", "eect", "entre", "will", "leur", "mais", "thse", "deux", "elle", "lanne", "chez", "left", "deux", "thus", "ainsi", "fait")) %>%
  mutate(word = stringi::stri_trans_general(word, "latin-ascii"))


colours <- c("#f44336", "#E91E63", "#9C27B0", "#673AB7", "#3F51B5", "#2196F3", "#03A9F4", "#00BCD4", "#009688", "#4CAF50", "#8BC34A", "#CDDC39", "#FFEB3B", "#FFC107", "#FF9800", "#FF5722", "#795548", "#9E9E9E")
colours <- c(colours, rep("#607D8B", length.out = nrow(data) - length(colours)))


data %>%
  arrange(desc(freq)) %>%
  mutate(
    word = factor(word, unique(word)),
    colours = colours,
    angle = 45 / 3 * sample(-2:2, n(), replace = TRUE, prob = c(1, 1, 4, 1, 1))
  ) %>%
  ggplot(aes(label = word, size = freq, color = word, angle = angle)) +
  scale_color_manual(values = colours) +
  ggwordcloud::geom_text_wordcloud(
    grid_margin = 0.5,
    area_corr = TRUE,
    area_corr_power = 1,
    mask = png::readPNG("img/brain.png"),
    rm_outside = TRUE
  ) +
  scale_size_area(max_size = 13) +
  theme_minimal()
```
</p>


## Scientific Impact <sub>*(retrieved on `r format(Sys.time(), "%d %B %Y")`)*</sub>


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
library(scholar)

stats <- scholar::get_profile("bg0BZ-QAAAAJ")
n_pub <- scholar::get_num_articles("bg0BZ-QAAAAJ")
n_cit <- sum(scholar::get_citation_history("bg0BZ-QAAAAJ")$cites)

# Vertical
knitr::kable(data.frame(
  Metric = c("Number of Publications", "Number of Citations", "h-index", "i10-index"),
  Score = c(n_pub, n_cit, stats$h_index, stats$h_index)
))

# # Horizontal
# knitr::kable(data.frame(
#   `Number of Publications` = n_pub,
#   n_citations = n_cit,
#   h_index = stats$h_index,
#   i10_index = stats$h_index
# ))
```



Cumulative citations and publication number, automatically scrapped from Google Scholar:

```{r impact, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.align='center'}
library(scholar)

stats <- scholar::get_publications("bg0BZ-QAAAAJ", flush = T) %>%
  dplyr::filter(year > 1950) %>%
  dplyr::group_by(year) %>%
  dplyr::summarise(
    Publications = n(),
    Citations = sum(cites)
  ) %>%
  dplyr::mutate(
    Publications = cumsum(Publications),
    Citations = cumsum(Citations)
  ) %>%
  dplyr::rename(Year = year) %>%
  tidyr::gather(Index, Number, -Year) %>% 
  dplyr::mutate(Index = fct_rev(Index))


p <- stats %>%
  ggplot(aes(x = Year, y = Number)) +
  geom_bar(aes(alpha=Year), stat="identity") +
  geom_line(aes(colour = Index), size = 2) +
  see::theme_modern() +
  ylab("") +
  # scale_x_continuous(breaks = seq(min(stats$Year), max(stats$Year), by = 1)) +
  scale_color_manual(values = c("#2196F3", "#E91E63")) +
  facet_wrap(~Index, scales = "free", strip.position = "top") +
  theme(
    strip.background = element_blank(),
    strip.placement = "outside",
    # strip.text.y = element_blank(),
    strip.text = element_text(face = "plain", size = 16),
    axis.title = element_text(face = "plain", size = 16),
    axis.title.x = element_blank(),
    legend.position = "none"
  )
p
```




## Collaboration Network

The data is retrieved from the Google Scholar co-author list, thus not 100% accurate (e.g., co-authors without a scholar profile are not listed).

```{r network, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10, fig.align='center', include=TRUE}
library(scholarnetwork)
library(scholar)
library(igraph)
library(ggraph)
library(tidygraph)

# Scholar
data <- scholar::get_coauthors("bg0BZ-QAAAAJ", n_coauthors=250, n_deep=1)

d <- data %>% 
  tidygraph::as_tbl_graph(directed=FALSE) %>%
  filter(name != "") %>% 
  mutate(closeness = tidygraph::centrality_closeness(normalized = TRUE),
         degree = tidygraph::centrality_degree(normalized = TRUE),
         betweeness = tidygraph::centrality_betweenness(normalized = TRUE)) %>%
  tidygraph::activate(edges) %>%
  mutate(importance = tidygraph::centrality_edge_betweenness(), 
         group = as.factor(from)) %>% 
  tidygraph::activate(nodes) %>%
  filter(!name %in% c("Sort By Citations", "Sort By Year", "Sort By Title")) %>% 
  mutate(name = stringr::str_remove(name, ",.*"),
         group = as.factor(tidygraph::group_edge_betweenness()),
         group2 = as.factor(tidygraph::group_optimal())) %>% 
  as.list()



# scholarnetwork
# d <- scholarnetwork::extractNetwork(id="bg0BZ-QAAAAJ", n=500)
# 
# d$nodes <- d$nodes %>%
#   mutate(name = label,
#          group = as.factor(group),
#          closeness = degree)
# 
# d$edges <- d$edges %>%
#   dplyr::filter(!grepl("D MAKOWSKI", node1) | !grepl("D MAKOWSKI", node2))



# Plot
p <- tidygraph::tbl_graph(nodes=d$nodes, edges=d$edges, directed=FALSE) %>% 
  ggraph::ggraph(layout = 'fr') +
  ggraph::geom_edge_arc(aes(alpha=importance), show.legend = FALSE, strength=0.1) +
  ggraph::geom_node_point(aes(size = degree, colour=group2), show.legend = FALSE) +
  ggraph::geom_node_text(aes(label = name, size=degree), repel = TRUE, check_overlap = TRUE, show.legend = FALSE) +
  ggraph::theme_graph() +
  scale_size_continuous(range = c(2, 6)) +
  see::scale_color_material_d(palette="rainbow", reverse=TRUE)
p
# ggsave("./img/network.png", p, height=10, width=10, dpi=600)
```



## Communications

### Publications

<p align="center">*2020*</p>

**Makowski, D.**, Pham, T., Lau Z. J., Leow D., Raine A., & Chen, S. H. *(under review)*. [The Structure of Deception: Validation of the Lying Profile Questionnaire](https://dominiquemakowski.github.io/publication/makowski2019heart/makowski2020structure.pdf).

<p align="center">*2019*</p>

**Makowski, D.**, Sperduti, M., Lavallée, S., Nicolas, S., & Piolino, P. (2019). [Adaptation and Validation of a Short French Version of the Affective Style Questionnaire](https://dominiquemakowski.github.io/publication/makowski2019heart/makowski2019adaptation.pdf). *International Journal of Cognitive Therapy*, 1-13.

**Makowski, D.**, Ben-Shachar, M. S., Chen, S. H., & Lüdecke, D. (2019). [Indices of Effect Existence and Significance in the Bayesian Framework](https://dominiquemakowski.github.io/publication/makowski2019heart/makowski2019indices.pdf). *Frontiers in Psychology, 10*, 2767.

**Makowski, D.**, Sperduti, M., Blondé, P., Nicolas, S., & Piolino, P. (2019). [The heart of cognitive control: Cardiac phase modulates processing speed and inhibition](https://dominiquemakowski.github.io/publication/makowski2019heart/makowski2019heart.pdf). *Psychophysiology*, e13490.

**Makowski, D.**, Ben-Shachar, M., & Lüdecke, D. (2019). [bayestestR: Describing effects and their uncertainty, existence and significance within the Bayesian framework](https://dominiquemakowski.github.io/publication/makowski2019bayestestr/makowski2019bayestestr.pdf). *Journal of Open Source Software*, 4(40), 1541.

Lüdecke, D., Waggoner, P., & **Makowski, D.** (2019). [insight: A unified interface to access information from model objects in R](https://dominiquemakowski.github.io/publication/ludecke2019insight/ludecke2019insight.pdf). *Journal of Open Source Software*, 4(38), 1412.

**Makowski, D.**, Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., & Piolino, P. (2019). [Phenomenal, Bodily and Brain Correlates of Fictional Reappraisal as an Implicit Emotion Regulation Strategy](https://dominiquemakowski.github.io/publication/makowski2019phenomenal/makowski2019phenomenal.pdf). *Cognitive, Affective, & Behavioral Neuroscience*, 19(4), 1-21.

**Makowski, D.**\*, Sperduti, M.\*, Lavallée, S., Nicolas, S. & Piolino, P. (2019). [Dispositional mindfulness attenuates the emotional attentional blink](https://dominiquemakowski.github.io/publication/makowski2019dispositional/makowski2019dispositional.pdf). *Consciousness & Cognition*, 67, 16–25.

<p align="center">*2018*</p>

**Makowski, D** (2018). [The psycho Package: An Efficient and Publishing-Oriented Workflow for Psychological Science](https://dominiquemakowski.github.io/publication/makowski2018psycho/makowski2018psycho.pdf). *Journal of Open Source Software*, 3(22), 470.


<p align="center">*2017*</p>

**Makowski, D.**, Dutriaux, L. (2017). [Neuropsydia.py: A Python Module for Creating Experiments, Tasks and Questionnaires](https://dominiquemakowski.github.io/publication/makowski2017neuropsydia/makowski2017neuropsydia.pdf), *Journal of Open Source Software*, 2(19), 259.

Tuena, C., Serino, S., Gaston-Bellegarde, A., Orriols, E., **Makowski, D.**, Riva, G. & Piolino, P. (2017). [How Virtual Embodiment Affects Episodic Memory Functioning: a Proof-of-Concept Study](https://dominiquemakowski.github.io/publication/tuena2017virtual/tuena2017virtual.pdf), *Annual Review of Cybertherapy and Telemedicine*, 15, 93-107.

Sperduti, M., Armougum, A., **Makowski, D.** & Piolino, P. (2017). [Interaction between attentional systems and episodic memory encoding: the impact of conflict on binding of information](https://dominiquemakowski.github.io/publication/sperduti2017interaction/sperduti2017interaction.pdf), *Experimental Brain Research*, 235(12), 3553-3560.

**Makowski, D.**\*, Sperduti, M.\*, Nicolas, S. & Piolino, P. (2017). ["*Being there*" and remembering it: Presence improves Memory Encoding](https://dominiquemakowski.github.io/publication/makowski2017being/makowski2017being.pdf). *Consciousness & Cognition*, 53, 194–202.

Nicolas, S., & **Makowski, D**. (2017). [Centenaire Ribot (I). La réception de l'oeuvre de Théodule Ribot chez l'éditeur Ladrange (1870-1873)](https://dominiquemakowski.github.io/publication/nicolas2017centenaire/nicolas2017centenaire.pdf). *Bulletin de Psychologie*, 70(3), 163-178.


Sperduti, M., **Makowski, D.**, Blondé, P. & Piolino, P. (2017). [Méditer pour bien vieillir ? Les possibles bienfaits des pratiques méditatives sur le déclin cognitif lié à l’âge | Meditation and successful aging: can meditative practices counteract age-related cognitive decline?](https://dominiquemakowski.github.io/publication/sperduti2017meditation/sperduti2017meditation.pdf), *Gériatrie et Psychologie Neuropsychiatrie du Vieillissement*, 15(2), 205-13.

Sperduti, M.\*, **Makowski, D.**\*, Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J. & Piolino, P. (2017). [The Distinctive Role of Executive Functions in Implicit Emotion Regulation](https://dominiquemakowski.github.io/publication/sperduti2017distinctive/sperduti2017distinctive.pdf). *Acta Psychologica*, 173, 13-20.

<p align="center">*2016*</p>

Nicolas, S., & **Makowski, D**. (2016). [Can mental fatigue be measured by Weber's compass? Alfred Binet's answer on the value of aesthesiometry (tactile sensitivity) as an objective measure of mental fatigue](https://dominiquemakowski.github.io/publication/nicolas2016can/nicolas2016can.pdf). *European Yearbook of the History of Psychology*, 2, 11-46.

Sperduti, M., **Makowski, D.**, & Piolino, P. (2016). [The protective role of long-term meditation on the decline of the executive component of attention in aging: a preliminary cross-sectional study](https://dominiquemakowski.github.io/publication/sperduti2016protective/sperduti2016protective.pdf). *Aging, Neuropsychology, and Cognition*, 23(6), 691-702.

Sperduti, M.\*, Arcangeli, M.\*, **Makowski, D.**, Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J. \& Piolino, P. (2016). [The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance](https://dominiquemakowski.github.io/publication/sperduti2016paradox/sperduti2016paradox.pdf). *Acta psychologica*, 165, 53-59.

<p align="center">*2015*</p>

**Makowski, D.**, Sperduti, M., Blanchet, S., Nicolas, S. & Piolino, P. (2015). [Régulation Emotionnelle face au Déclin Cognitif dans le Vieillissement : Un Faux Paradoxe ? | Emotion regulation and the cognitive decline in aging: beyond the paradox](https://dominiquemakowski.github.io/publication/makowski2015emotion/makowski2015emotion.pdf). *Gériatrie et Psychologie Neuropsychiatrie du Vieillissement*, 13(3), 301-8.

<sup>*Note: Electronic versions are provided to ensure timely dissemination of academic work. They can be downloaded for noncommercial purposes. Copyright resides with the respective copyright holders as stated in each article. The files may not be reposted without permission from copyright holders.*</sub> 

<sup>*Disclaimer: This page is for personal friends only so people that will download the papers are my peers and friends. As a consequence, the papers are not shared with strangers.*</sub> 


### General Audience / Media Coverage

- Pint of Science, ["Back to the Matrix : pilule bleue ou rouge ?"](https://pintofscience.fr/event/back-to-the-matrix--pilule-bleue-ou-rouge-). 16 May 2018, Paris, France.
- Public Debate, [*Art & science discussion on sensory illusions*](http://www.facts-bordeaux.fr/FESTIVAL/Programme/Agenda-2017/Rencards-du-savoir-Les-illusions-sensorielles). 24 November 2017, Bordeaux, France.
- Magazine, [*Neuroanatomie de la réalité : quand le réel n’est plus*](https://biblineuropsy.com/2016/04/19/les-yeux-brouilles/). 2016, Les yeux brouillés, 1, 48-55.
- National TV, [*The effect of violent images on the brain and body*](https://www.youtube.com/watch?v=ihGs1V9kz4w). 2015, Testé sous contrôle médical, France 4
- Online journal, [*”Avengers, l’ère d’Ultron” en 3D : aussitôt vu, aussitôt oublié ?*](http://blog.francetvinfo.fr/actu-cine/2015/05/07/avengers-lere-dultron-en-3d-aussitot-vu-aussitot-oublie.html) 2015, francetvinfos.fr


### Talks

<p align="center">*2018*</p>

**Makowski, D.**, Sperduti, M., Nicolas, S. & Piolino, P. (2017). *Interindividual Determinants of Emotion Regulation through Fiction*. 2ème Congrès Francophone de TCC, 14-16 June, Geneva, Switzerland.

**Makowski, D.** (2018, *invited*). *How Reality can Modulate Memory and Emotions*. CRPCPO's monthly seminar, 23 March, Amiens, France.

**Makowski, D.**, Sperduti, M., Nicolas, S. & Piolino, P. (2018). *Engagement in Fiction as an Altered State of Consciousness*. 6th Mind, Brain & Body Symposium, 15-16 March, Berlin, Germany.

<p align="center">*2017*</p>

**Makowski, D.**, Sperduti, M., Nicolas, S. & Piolino, P. (2017). *Vers la thérapie neurocognitive ? L’apport des neurosciences affectives dans la TCC*. 45ème congrès de l’AFTCC, 14-16 December, Paris, France.

Sperduti, M., **Makowski, D.** & Piolino, P. (2017). *The Role of Self-Relevance and Interindividual Variability in Executive Functions in Implicit Emotion Regulation*. International Society for the Study of Interindividual Differences (ISSID), 24-28 July, Warsaw, Poland.


**Makowski, D.**, Sperduti, M. & Piolino, P. (2017). *The Distinctive Effect of Emotion Regulation andMindfulness on Attentional Capture*. 1ère Journée Scientifique des Jeunes Chercheurs du Centre de Recherches sur la Cognition et l’Apprentissage, 8 June, Poitiers, France.

<p align="center">*2016*</p>

**Makowski, D.**, Sperduti, M. & Piolino, P. (2016).*”Being there” and Remembering it: Presence en-hances Encoding in Memory*. International Congress On Memory (ICOM), 17-22 July, Budapest, Hungary.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2016). *The Sense of Reality as a feature of proto-Consciousness, its Alteration and Generation induced by Fictional Worlds*. Literary States of Consciousness, 2 June, Paris, France.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2016). *Does Mindfulness ability differently affect Implicit and Explicit Emotion Regulation?* 2nd International Conference on Mindfulness (ICM), 11-15 May, Roma, Italy.

Sperduti, M., **Makowski, D.** & Piolino, P. (2016). *Does mindfulness enhance interoception? Dissociation between different interoceptive abilities*. 2nd International Conference on Mindfulness, 11-15 May, Roma, Italy.

<p align="center">*2015*</p>

**Makowski, D.**, Sperduti, M. & Piolino, P. (2015). *Bon et Mauvais Régulateurs Emotionnels: Un Rôle Spécifique de l’Inhibition ?* 56è Congrès National de la Société Française de Psychologie (SFP), 2-4 September, Strasbourg, France.

**Makowski, D.**, Sperduti, M., Pelletier, J. & Piolino, P. (2015). *Régulation émotionnelle et Self Control : De la recherche Fondamentale à l’Application Clinique*. 1er Congrès Francophone de TCC, 27-29 May, Lyon, France.

<p align="center">*2014*</p>

**Makowski, D.**, Sperduti, M., Arcangeli, M., Pelletier, J. & Piolino, P. (2014). *From Philosophy to the Rehabilitation of Psychiatric Patients: Fiction/Reality, Emotion et Cognitive Control*. Journée d’hiver de l’IUPDP, 19 December, Boulogne-Billancourt, France.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2014). *L’émotion face à la fiction : l’étude de patientsschizophrènes éclaire le paradoxe de la fiction*. 27 June, Fête de la Recherche, Boulogne-Billancourt,France.

<p align="center">*2013*</p>

**Makowski, D.**, & Rossi, S. (2013). [*Le jugement esthétique chez l’enfant*](https://www.youtube.com/watch?v=Hvs7t5G_dLM). Journées Neurosciences, Esthétique, et Complexité, 28 September, Paris, France.



